### 2016-01-17 urban_boundaries_gb/Twitter_Urban_Boundary.tex
new version emerged from Austin's edit

The power of using Twitter user mobility to delineate natural boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the users collective distribution. 
In addition, the distance range of the movements usually could be explained by local socioeconomic factors (e.g., work commuting ), which could provide some specific interpretation of the apparent patterns.
The patterns obtained from Twitter users mobility patterns are comparable to the patterns produced by division the network of landline phone call~\cite{ratti2010}.\
For example, the region of Wales appeared to consists of three communities as found by connectivity of both phone calls and long distance movements. 
However, the regions extracted from the mobility network seems to be more spatially consistent with minimum spatial gaps compared to the partitions extracted from land-line calls networks in Great Britain~\cite{ratti2010}.

@@

%\subsection*{xx}
%see \nameref{S1_Fig}.
%
%\section*{Supporting Information}
%
%% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
%\subsection*{S1 A scalable data processing framework}
%\label{S1_framework}

@@

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
\begin{thebibliography}{10}
\bibitem{schliephake}
Schliephake, C., 2014. Urban Ecologies: City Space, Material Agency, and Environmental Politics in Contemporary Culture. Lexington Books.

>>>>

The power of using Twitter user mobility to delineate natural boundaries is the ability to redraw the city at different mobility ranges inferred objectively from the users collective distribution. 
In addition, the distance range of the movements usually could be explained by local socioeconomic factors (e.g., work commuting ), which could provide some specific interpretation of the apparent patterns.
The patterns obtained from Twitter users mobility patterns are comparable to the patterns produced by division the network of landline phone call~\cite{ratti2010}.
For example, the region of Wales appeared to consists of three communities as found by connectivity of both phone calls and long distance movements. 
However, the regions extracted from the mobility network seems to be more spatially consistent with minimum spatial gaps compared to the partitions extracted from land-line calls networks in Great Britain~\cite{ratti2010}.

@@

@@

\begin{thebibliography}{10}
\bibitem{schliephake}
Schliephake, C., 2014. Urban Ecologies: City Space, Material Agency, and Environmental Politics in Contemporary Culture. Lexington Books.
